\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-30 paper/main.tex

We developed \name as a computational model to predict drug--target
interactions. Specifically, given a protein, \name will identify and
rank drugs that likely target this protein. \name combines two 
types of features: structural information for drugs and proteins that
can be used to determine if they may physically interact, and

>>>>

We developed \name as a computational model to predict drug--target
interactions. Specifically, given a protein, \name will identify and
rank drugs that likely target this protein. \name combines two 
types of features: structural information for drugs and proteins that
can be used to determine if they may physically interact, and
information about drug effects that may localize on an interaction
network.
